\chapter{System Analysis and Design}
\ifpdf
    \graphicspath{{Chapter2/Chapter2Figs/PNG/}{Chapter2/Chapter2Figs/PDF/}{Chapter2/Chapter2Figs/}}
\else
    \graphicspath{{Chapter2/Chapter2Figs/EPS/}{Chapter2/Chapter2Figs/}}
\fi


All of the computations and graphics in this project are implemented using the Open Source statistical software R.\cite{R-cite}

\section{Introduction to R}

R is a free software programming language and software environment for statistical computing and graphics.
It is an implementation of the S programming language combined with lexical scoping semantics inspired by Scheme.
S was created by John Chambers while at Bell Labs. R was created by Ross Ihaka and Robert Gentleman
at the University Of Auckland, New Zealand, and is currently developed by the R Development Core Team.
R is a GNU project. The source code for the R software environment is written primarily in C, FORTRAN, and R.

R is especially suited to implement the statistical methods needed for network analysis. It provides a wide
variety of statistical and graphical techniques, including linear and nonlinear modelling, classical statistical tests,
time-series analysis, classification, clustering. Further, it is easily extensible through functions and extensions,
and the R community is noted for its active contributions in terms of packages.
Many of R’s standard functions are written in R itself, which makes it easy for users to follow the algorithmic choices made.
For computationally intensive tasks, C, C++, and FORTRAN code can be linked and called at run time.

\noindent {\bf The R Environment}

R is an integrated suite of software facilities for data manipulation, calculation and graphical display. Among other things it has
\begin{itemize}
\item An effective data handling and storage facility,
\item A suite of operators for calculations on arrays, in particular matrices,
\item A large, coherent, integrated collection of intermediate tools for data analysis, graphical facilities for data analysis and display either directly at the computer or on hard- copy, and
\item A well developed, simple and effective programming language which includes conditionals, loops, user defined recursive functions and input and output facilities.
\end{itemize}

R can be used as an environment within which many classical and modern statistical techniques have been implemented.
A few of these are built into the base R environment, but many are supplied as packages. There are about 25 packages
supplied with R (called standard and recommended packages) and many more are available through the CRAN family of
Internet sites (via http://CRAN.R-project.org).

All R functions and datasets are stored in packages. Only when a package is loaded are its contents available.
This is done both for efficiency (the full list would take more memory and would take longer to search than a subset),
and to aid package developers, who are protected from name clashes with other code.
Some of the R packages used in this project are Igraph, statnet, sna, ProNet and ergm.


% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
