
% Thesis Abstract -----------------------------------------------------


%\begin{abstractslong}    %uncommenting this line, gives a different abstract heading
\begin{abstracts}        %this creates the heading for the abstract page

This project focuses on analysis of data related to social interaction among individuals in Free
and Open Source Software ecosystem. Undoubtedly this has emerged as a socially
important big data problem in recent times. The analysis discussed here includes four main topics,
namely, Weight Assignment, Influence Analysis, Link Prediction and Time Series Analysis.
Weight Assignment involves enhancement of the network structure in order to obtain
a real world perspective. On the other hand, Influence Analysis identifies the highly influential
individuals among the entities in a social network. Link Prediction deals with predicting
the most probable interactions in the future among individuals using already existing
interactions. Since social networks are not stationary objects, Time Series Analysis
is a dynamic approach used to formally understand the growth of
a network over time. These concepts are illustrated with analysis of certain large
social networks. Since the emphasis currently is on big data, a new technique based
on random sampling of subnetworks from very large networks is developed and tested.
All the computations and algorithms have been implemented on R and have been tested on a number of 
large datasets. Improvements in performance have been observed compared to existing methods. 
\end{abstracts}
%\end{abstractlongs}


% ----------------------------------------------------------------------


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
