\chapter{Legal Code of License}
\label{license}


THE WORK (AS DEFINED BELOW) IS PROVIDED UNDER THE TERMS OF THIS CREATIVE COMMONS PUBLIC LICENSE (``CPL'' OR ``LICENSE''). THE WORK IS PROTECTED BY COPYRIGHT AND/OR OTHER APPLICABLE LAW. ANY USE OF THE WORK OTHER THAN AS AUTHORIZED UNDER THIS LICENSE AND/OR COPYRIGHT LAW IS PROHIBITED.

BY EXERCISING ANY RIGHTS TO THE WORK PROVIDED HEREIN, YOU ACCEPT AND AGREE TO BE BOUND BY THE TERMS OF THIS LICENSE. THE LICENSOR GRANTS YOU THE RIGHTS CONTAINED HERE IN CONSIDERATION OF YOUR ACCEPTANCE OF SUCH TERMS AND CONDITIONS.

\begin{enumerate}
 \item {Definitions}
    \begin{enumerate}
       \item {``Collective Work'' means a work, such as a periodical issue, anthology or encyclopedia, in which the Work in its entirety in unmodified form, along with a number of other contributions, constituting separate and independent works in themselves, are assembled into a collective whole. A work that constitutes a Collective Work will not be considered an Adaptation (as defined below) for the purposes of this License.}
        \item { ``Adaptation'' means a work based upon the Work or upon the Work and other preexisting works, such as a translation, musical arrangement, dramatization, fictionalization, motion picture version, sound recording, art reproduction, abridgment, condensation, or any other form in which the Work may be recast, transformed, or adapted, and includes:}
	  \begin{enumerate}
	  \item {in relation to a dramatic Work, the conversion of the work into a non-dramatic work;}
	  \item {in relation to a literary Work or an artistic Work, the conversion of the Work into a Work by way of performance in public or otherwise;}
	  \item {in relation to a literary or dramatic Work, any abridgement of the Work or any version of the Work in which the story or action is conveyed wholly or mainly by means of pictures in a form suitable for reproduction in a book, or in a newspaper, magazine or similar periodical;}
	  \item{in relation to a musical Work, any arrangement or transcription of the Work; and}
	  \item{in relation to any Work, any use of such work involving its re-arrangement or alteration.}
	  \end{enumerate}
      \item {``Licensor'' means the individual/s and/or entities who own/s all rights, title and interests, including copyright in a Work and offers the Work under the terms of this License.}
      \item{ ``Author'' means:}

	  \begin{enumerate}
	  \item {in relation to a literary or dramatic work, the author of the work;}
	  \item{in relation to musical work, the composer;}
	  \item{in relation to an artistic work other than a photograph, the artist;}
	  \item{in relation to a photograph, the person taking the photograph;}
	  \item{in relation to a cinematograph film or sound recording, the producer; and}
	  \item{in relation to any literary, dramatic, musical or artistic work which is computer-generated, the person who causes the work to be created.}
	  \end{enumerate}

      \item{``Work'' means any work as defined under the Copyright Act, 1957, which is offered under the terms of this License.}
      \item{``You'' means an individual/s and/or entity exercising rights under this License who has not previously violated the terms of this License with respect to the Work, or who has received express permission from the Licensor to exercise rights under this License despite a previous violation.}
      \item{``Licence Elements'' means the following high-level license attributes as selected by the Licensor and indicated in the title of this License: Attribution-NonCommercial 2.5}
      \item{``Phonorecords'' means any technology that enables musical works and sound recordings to be played, recorded and stored in digital format for use on computers or other devices.}
    \end{enumerate}

  \item{Fair Dealing Rights. Nothing in this license is intended to reduce, limit, or restrict any rights arising from any fair dealing, statutory right, first sale or other limitations on the exclusive rights of the copyright owner under copyright law or other applicable laws.}

  \item{Licence Grant. Subject to the terms and conditions of this License, Licensor hereby grants You, in consideration of You exercising the rights, a worldwide, royalty-free, non-exclusive, perpetual (for the duration of the applicable copyright) license to exercise the rights in the Work as stated below:}

      \begin{enumerate}
       \item {to reproduce the Work, to incorporate the Work into one or more Collective Works, and to reproduce the Work as incorporated in the Collective Works;}
	\item {to create and reproduce Adaptations of the Work;}
	\item {to distribute copies or, display or perform publicly including by means of a digital audio transmission, the Work, including as incorporated in Collective Works;}
	\item {to distribute copies of, display, communicate to the public or perform publicly, including by means of a digital audio transmission the Adaptations of the Work;}
	\item {The above rights may be exercised in all media and formats whether now known or hereafter devised. The above rights include the right to make such modifications as are technically necessary to exercise the rights in other media and formats. All rights not expressly granted by Licensor are hereby reserved, including but not limited to the rights set forth in Section 4, below.}
      \end{enumerate}
    
  \item{Restrictions. The license granted in Section 3, above, is expressly made subject to and limited by the following restrictions:}

      \begin{enumerate}
       \item {You may reproduce, distribute, publicly display, publicly perform, communicate the Work, publicly digitally perform the Work or create an adaptation of the Work only under the terms of this License and You must include a copy of this License, or the Uniform Resource Identifier for this License with every copy or phonorecord of the Work You distribute, publicly display, publicly perform, or publicly digitally perform. You may not offer or impose any terms on the Work that alter or restrict the terms of this License or the recipients' exercise of the rights granted hereunder. You may not sublicense the Work. You must keep intact all notices that refer to this License and to the disclaimer of warranties. You may not distribute, publicly display, publicly perform, or publicly digitally perform the Work with any technological measures that control access or use of the Work in a manner inconsistent with the terms of this License Agreement. The above applies to the Work as incorporated in a Collective Work, but this does not require the Collective Work apart from the Work itself to be made subject to the terms of this License. If You create a Collective Work, upon notice from the Licensor, You must, to the extent practicable, remove from the Collective Work any credit as required by Clause 4(c), as requested. If You create an Adaptation, upon notice from the Licensor, You must, to the extent practicable, remove from the Adaptation any credit as required by Clause 4(c) as requested.}
	\item {You may not exercise any of the rights granted to You in Section 3 above in any manner that is primarily intended for or directed toward commercial advantage or private monetary compensation. The exchange of the Work for other copyrighted works by means of digital file-sharing or otherwise shall not be considered to be intended for or directed toward commercial advantage or private monetary compensation, provided there is no payment of any monetary compensation in connection with such an exchange of copyrighted works.}
	\item {If you distribute, publicly display, publicly perform, or publicly digitally perform the Work or any Adaptation or Collective Works, You must keep intact all copyright notices for the Work and provide, reasonable to the medium or means You are utilizing, the following:}
	    \begin{enumerate}
	     \item{the name of the Author (or pseudonym, if applicable) if supplied, and/or;}
	      \item{if the Author and/or Licensor designates another party or parties (e.g. a sponsor institute, publishing entity or journal) for attribution in the Licensor's copyright notice, terms of service or by other reasonable means, the name of such party or parties;}
	      \item{the title of the Work if supplied;}
	      \item{to the extent reasonably practicable, the Uniform Resource Identifier, if any, that Licensor specifies to be associated with the Work, unless such Uniform Resource Identifier does not refer to the copyright notice or licensing information for the Work;and}
	      \item{in the case of an Adaptation, a credit identifying the use of the Work in the Adaptation (e.g., ``Hindi translation of the Work by Author,'' or ``Screenplay based on original Work by Author``). Such credit may be implemented in any reasonable manner. It is provided, however, that in the case of an Adaptation or Collective Work, at a minimum, such credit must appear where any other comparable authorship credit appears and in a manner at least as prominent as such other comparable authorship credit.}
	    \end{enumerate}
      \end{enumerate}

    \item{Representations, Warranties and Disclaimer.}
	\begin{enumerate}
	  \item {UNLESS OTHERWISE MUTUALLY AGREED TO BY THE PARTIES IN WRITING, THE LICENSOR OFFERS THE WORK AS-IS AND MAKES NO REPRESENTATIONS OR WARRANTIES OF ANY KIND CONCERNING THE WORK, EXPRESS, IMPLIED, STATUTORY OR OTHERWISE, INCLUDING, WITHOUT LIMITATION, WARRANTIES OF TITLE, MERCHANTIBILITY, FITNESS FOR A PARTICULAR PURPOSE, NONINFRINGEMENT, OR THE ABSENCE OF LATENT OR OTHER DEFECTS, ACCURACY, OR THE PRESENCE OF ABSENCE OF ERRORS, WHETHER OR NOT DISCOVERABLE. SOME JURISDICTIONS DO NOT ALLOW THE EXCLUSION OF IMPLIED WARRANTIES, SO SUCH EXCLUSION MAY NOT APPLY TO YOU.}
	  \item{YOU WARRANT THAT YOU ARE THE COPYRIGHT HOLDER OF THE CONTRIBUTIONS WHEN YOU SUBMIT THEM TO CREATIVE COMMONS.}
	\end{enumerate}
    
    \item{Limitation on Liability.}
  
    EXCEPT TO THE EXTENT REQUIRED BY APPLICABLE LAW, IN NO EVENT WILL THE LICENSOR BE LIABLE TO YOU ON ANY LEGAL THEORY FOR ANY SPECIAL, INCIDENTAL, CONSEQUENTIAL, PUNITIVE OR EXEMPLARY DAMAGES ARISING OUT OF THIS LICENSE OR THE USE OF THE WORK, EVEN IF THE LICENSOR HAS BEEN ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.
  
    
    \item{Termination.}
      \begin{enumerate}
       \item {This License and the rights granted hereunder will terminate automatically upon any breach by You of the terms of this License. Individuals or entities who have received Adaptations or Collective Works from You under this License however, will not have their licenses terminated provided such individuals or entities remain in full compliance with their licenses. Sections 1, 2, 5, 6, 7, and 8 will survive any termination of this License.}
	\item{Subject to the above terms and conditions, the license granted here is perpetual (for the duration of the applicable copyright in the Work). Notwithstanding the above, the Licensor reserves the right to release the Work under different license terms or to stop distributing the Work at any time; provided, however that any such release under different license terms or cessation of distribution of the Work will not serve to withdraw this License (or any other license that has been, or is required to be, granted under the terms of this License), and this License will continue in full force and effect unless terminated as stated above.}
      \end{enumerate}

    \item{Miscellaneous.}
	\begin{enumerate}
	\item {Each time You distribute or publicly digitally perform the Work or a Collective Work, the Licensor offers to the recipient a license to the Work on the same terms and conditions as the license granted to You under this License.}
	\item {Each time You distribute or publicly digitally perform a Adaptation, Licensor offers to the recipient a license to the original Work on the same terms and conditions as the license granted to You under this License.}
	\item {If any provision of this License is invalid or unenforceable under applicable law, it shall not affect the validity or enforceability of the remainder of the terms of this License, and without further action by the parties to this agreement, such provision shall be reformed to the minimum extent necessary to make such provision valid and enforceable.}
	\item {No term or provision of this License shall be deemed waived and no breach consented to unless such waiver or consent shall be in writing and signed by the party to be charged with such waiver or consent.}
	\item {This Licence constitutes the entire agreement between the parties with respect to the Work licensed here. To the full extent permitted by applicable law, there are no understandings, agreements or representations with respect to the Work not specified here. Licensor shall not be bound by any additional provisions that may appear in any communication from You. This Licence may not be modified without the mutual written agreement of the Licensor and You.}
	\item {Words and Phrases not defined herein shall to be extent possible have the same meaning as given to them in the Copyright Act, 1957.}
	\item {This agreement shall be deemed to be a contract made in India and shall be construed and applied in all respects in accordance with Indian law and the parties hereto submit and agree to the jurisdiction of the Indian courts.}
	\end{enumerate}

\end{enumerate}

\begin{flushleft}
 \textbf{Disclaimer\\}
\end{flushleft}

CREATIVE COMMONS CORPORATION IS NOT A LAW FIRM AND DOES NOT PROVIDE LEGAL SERVICES. DISTRIBUTION OF THIS LICENSE DOES NOT CREATE A LAWYER-CLIENT RELATIONSHIP. CREATIVE COMMONS PROVIDES THIS INFORMATION ON AN "AS-IS" BASIS. CREATIVE COMMONS MAKES NO WARRANTIES REGARDING THE INFORMATION PROVIDED, AND DISCLAIMS LIABILITY FOR DAMAGES RESULTING FROM ITS USE. 

Creative Commons is not a party to this License, and makes no warranty whatsoever in connection with the Work. Creative Commons will not be liable to You or any party on any legal theory for any damages whatsoever, including without limitation any general, special, incidental or consequential damages arising in connection to this license. Notwithstanding the foregoing two (2) sentences, if Creative Commons has expressly identified itself as the Licensor hereunder, it shall have all the rights and obligations of a Licensor.

Except for the limited purpose of indicating to the public that the Work is licensed under the CCPL, neither party will use the trademark "Creative Commons" or any related trademark or logo of Creative Commons without the prior written consent of Creative Commons. Any permitted use will be in compliance with Creative Commons' then current trademark usage guidelines, as may be published on its website or otherwise made available upon request from time to time.

Creative Commons may be contacted at http://creativecommons.org/.


% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
